---
title: "R Notebook: oWell-Part 3"
author: "Sarah Ronchetti | 11515255"
output: html_notebook
---

```{r}

library("ggplot2")

```

##Here we are setting up our Git remote and Git local to access the data 
```{r}
which.github = "remote";
github.local = "~/Desktop/WSU_STATS419_2021/sronchet/";
github.remote = "https://raw.githubusercontent.com/sronchet/WSU_STATS419_2021/main/sronchet/";

if(which.github == "remote")
{
  mypath = paste0(github.remote,"workspace/o-well");
}else{
  mypath = paste0(github.local,"workspace/o-well");
}

```


```{r}
path.data = paste0(mypath, "/data/")
owell.metals = read.delim(paste0(path.data,"owell.metals.txt"), header = TRUE, sep="|");
owell.chemistry = read.delim(paste0(path.data, "owell.chemistry.txt"), header = TRUE, sep="|");
well.location = read.delim(paste0(path.data, "wells-location.txt"), header= TRUE, sep = "|");
well.location.north = read.delim(paste0(path.data, "wells-location-north.txt"), header=TRUE, sep="|");
well.location.south = read.delim(paste0(path.data, "wells-location-south.txt"), header= TRUE, sep="|");
```

```{r}

#building data object
owell.metals$latitude = well.location$latitude;
owell.metals$longitude = well.location$longitude;
owell.metals$altitude.ft = well.location$altitude.ft;
owell.metals$fault = well.location$fault;
owell.metals$geology = well.location$geology;

owell.chemistry$latitude = well.location$latitude;
owell.chemistry$longitude = well.location$longitude;
owell.chemistry$altitude.ft = well.location$altitude.ft;
owell.chemistry$fault = well.location$fault;
owell.chemistry$geology = well.location$geology;

wells = list(); 
  wells$saudi = list(); 
  wells$saudi$metals = owell.metals;
  wells$saudi$chemistry = owell.chemistry;

```

```{r}
storeToPipe = function(df, file, header=TRUE, quote="", sep="|", row.names = FALSE)
{
  if(quote == "")
  {
    quote = FALSE;
  }
  utils::write.table(df, file=file, quote = quote, col.names = header, row.name = row.names, sep = sep);
}

readFromPipe = function(file,header=TRUE, quote="", sep="|")
{
  utils::read.csv(file,header=header, quote=quote,sep=sep);
}

```

#owell 3
##The scatterplot below displays the data found between the latitude and the geology (type of rock). 
```{r}
ggplot(well.location, aes(x=geology, y=latitude))+geom_point()+theme(axis.text.x=element_text(angle=90))+ggtitle("Scatter Plot Comparing Geology to Latitude")+(theme(plot.title = element_text(hjust = 0.5)))

```

##The scatterplot below displays the data found between the longitude and the geology (type of rock).
```{r}
ggplot(well.location, aes(x=geology, y=longitude))+geom_point()+theme(axis.text.x=element_text(angle=90))+ggtitle("Scatter Plot Comparing Geology to Longitude")+(theme(plot.title = element_text(hjust = 0.5)))

```

#owell 2
##In this histogram I am showing on the x-axis the data I gathered for the faults in the north. On the y-axis it is showing the frequency of the data provided. 
```{r}

hist(well.location.north$fault, xlab="Faults in the North", ylab= "Frequency", main = "Histogram of the Frequency of Faults in the North"); 

```

##In the next histogram I am displaying similar data as the histogram above, except I am showing the faults and the frequency that occurs in the south of Saudi Arabia 
```{r}

hist(well.location.south$fault, xlab="Faults in the South", ylab= "Frequency", main = "Histogram of the Frequency of Faults in the South");


```
